### 2017-10-31 submission/manuscript.tex
change title

\section{The Importance of the Microbiota and Individual Community
Members in Colorectal
Cancer}\label{the-importance-of-the-microbiota-and-individual-community-members-in-colorectal-cancer}

>>>>

\section{The Microbiota and Individual Community Members in Colorectal
Cancer: Is There a Common
Theme?}\label{the-microbiota-and-individual-community-members-in-colorectal-cancer-is-there-a-common-theme}
